---
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    template: ./resources/aog-latex-ms.tex
  word_document:
    reference_docx: ./resources/aog_word_style.docx
fontfamily: mathpazo
fontsize: 11pt
anonymous: false
endnotes: false
pagenumber: 1
bibliography: ../project.bib
biblio-style: ./resources/ajs.bst
title: "The Title"
author:
- affiliation: University of Oregon, Sociology
  name: Aaron Gullickson
- affiliation: Some Research University
  name: My co-author
keywords: keywords
thanks: Thanks to people and stuff
abstract: This is a test abstract
---

```{r, include=FALSE}
load("../../analysis/output/analytical_data.RData")
library(haven)
library(ggplot2)
library(knitr)
library(texreg)
library(tinytex)
```

# Introduction

In movies and television shows, we constantly see parents, friends, neighbors, and others judge an individual for coming out as queer or finding out they were queer. It gives queer individuals a false sense of what actually happens when coming out to peers. Although the movies may make it seem like a scary experience, in reality nowadays, it is a breath of fresh air. In 2010, however, our society was inbetween whether or not it supported queer indiviudals. America was almost split with a few more leaning in the support same sex indiviudals and relationships. This survey was created to see how the LGBT community felt being around society. Queer individuals coming out to their peers will feel more support, happiness, and overall enjoyment in life because they are able to be who they are. This data should show that although society is not perfect and has not fully accepted the queer community, there has been a lot of process made. The data is from 2010 so we should be able to notice a difference in how individuals felt then compared to how we see the queer community act today. Using this data we are going to analyze the overall happiness of individuals that disclose their sexual identity with neighbors, family, and friends.

# Background


# Data and Methods

The data was collected using self reported surveys in 2010. The original survey was a 105 item survey and was administered to over 5000 people. The strategy of data collection was through a variety of strategies, includng: venue-based sampling at strategic events, snowball sampling, respondent-driven sampling, and the internet. The initial data set comprised of 4953 observations and 304 variables from all sexual identities. After recoding and subsetting, we ended with 10 variables and 3241 observations and 10 variables and only accounted for LGBT responses, not heterosexual responses. This is due to someone being heterosexual and being asked who they came out to which does not make sense. 

Happiness was a combination of two questions: Over the past week, how many times have you felt happy and how many times have you enjoyed life? These we felt were similar so we combined them and subtracted two to make zero our base start. This is our dependent variable for our analysis. We combined another variable from two other questions: How connected do you feel to the LGBT community as a whole and how strong is your bond with others in the LGBT community? We used the same technique as the happiness variable and subtracted two to make our zero our base start. Other variables such as coming out to friends, family, and neighbors were given named labels rather than a numbered order. The same sex marriage and military data was given a true or false code rather than a 1 or 0 code. The rest of the data was left in numbered variables with a different variable name that makes it easier to understand. All the data but the two true or false variables were conducted using a 4,5, or 6-point likert scales making them ordinal variables. To focus on the LGBT community data, anyone who responded as straight was dropped from the subsetted data. This would help reduce biases from possible anti-LGBT thoughts or ideas from straight individuals especially since it is before being LGBT was accepted. 

We calculated some univariate models to better understand what a few of our variables looked like before running mean difference boxplots. In figure 1, we see that a majority of people came out to all of their family members while some and most as well as none and about half were faily equal in responses. Figure 2 was a comparative barplot to show the percentage of individuals who support same sex marriage and military members. The results were less than I had anticiapted. Only around 95% said they are in support. Since we did remove heterosexual data from the datasets, one would have expected at least 99%, if not 100%, of individuals would be in favor of both same sex marriage and mititary members. In figure 3, the histogram shows that individuals are happy a lot (4) to most (6) of the time while very few are never (0) or somtimes (2) happy. Being that this data is from 2010, this is great becasue 2010 was a struggle for the LGBT community to really be recognized as equal to heterosexual community. It shows the positive views that the LGBT community has in a darker period of time. In figure 4, we show the support of family members for LGBT members. The histogram shows that family members are supportive of LGBT members and there is a steady decline on the left tail since we are reaching zero.  

# Results


# Conclusions

# References

```{r textreg, results="asis", echo=FALSE}
model1 <- lm(happiness~fam_support, data=sjsd)
model2 <- lm(happiness~fam_support+out_family, data=sjsd)
model3 <- lm(happiness~fam_support*out_family+out_friends+out_neighbors+lgbt_bond+neigh_phobia+event,
             data=sjsd)
```


```{r barplot1, echo=FALSE}
ggplot(sjsd, aes(x=out_family))+
  geom_bar()+
  labs(x="Coming out to family members", y="Frequency", title="Distribution of coming out to family members")+
  theme_bw()
```

```{r compbarplot1, echo=FALSE, fig.cap= Figure 1: The support for same sex marriage and military members in the SJSD 2010 dataset.}
percent <- cbind(prop.table(table(sjsd$marriage)), prop.table(table(sjsd$military)))*100
barplot(percent, beside=TRUE, names.arg=c("Same-sex military","Gay marriage"), 
        las=1, main="Support same sex marriage and military members", ylab="Percent of reponses for support",
        col=c("darkgreen", "yellow"), legend.text=c("No","Yes"), cex.names="0.7")
```

```{r histogram1, echo=FALSE}
ggplot(sjsd, aes(happiness))+
  geom_histogram(binwidth=1, col="black")+
  labs(x="Happiness experienced",y="Frequency",title="Histogram of happiness experienced")+
  theme_bw()
```

```{r histogram2, echo=FALSE}
ggplot(sjsd, aes(fam_support))+
  geom_histogram(binwidth=1, col="green")+
  labs(x="LGBT family support",y="Frequency",title="Histogram of family support for LGBT members")+
  theme_bw()
```


```{r boxplot1, echo=FALSE}
ggplot(sjsd, aes(x=reorder(out_family, happiness, median), y=fam_support))+
  geom_boxplot(fill="gray", outlier.color = "black", varwidth = TRUE)+
  labs(x="Coming out to family members", y="Family support", title="Boxplot of family support after coming out to family members")+
  coord_flip()+
  theme_bw()
```


```{r boxplot2, echo=FALSE}
ggplot(sjsd, aes(x=reorder(out_family, happiness, median), y=happiness))+
  geom_boxplot(fill="skyblue", outlier.color = "red", varwidth = TRUE)+
  labs(x="Coming out to family members", y="Happiness experienced", title="Boxplot of happiness experienced after coming out to family members")+
  coord_flip()+
  theme_bw()
```

```{r boxplot3, echo=FALSE}
ggplot(sjsd, aes(x=out_neighbors, y=neigh_phobia))+
  geom_boxplot(fill="yellow", outlier.color = "green", varwidth = TRUE)+
  labs(x="Coming out to neighbors", y="Neighborhood phobia", title="Boxplot of coming out to neighbors and homophobia in the neighborhood")+
  coord_flip()+
  theme_bw()
```


```{r boxplot4, echo=FALSE}
ggplot(sjsd, aes(x=out_neighbors, y=happiness))+
  geom_boxplot(fill="orange", outlier.color = "blue", varwidth = TRUE)+
  labs(x="Coming out to neighbors", y="Happiness experienced", title="Boxplot of coming out to neighbors and happiness")+
  coord_flip()+
  theme_bw()
```


```{r boxplot5, echo=FALSE}
ggplot(sjsd, aes(x=event, y=lgbt_bond))+
  geom_boxplot(fill="red", outlier.color = "green", varwidth = TRUE)+
  labs(y="Bond felt with LGBT community", x="Participates in LGBT events", title="Boxplot of LGBT events attended and\nthe bond felt with LGBT community")+
  coord_flip()+
  theme_bw()
```


```{r boxplot6, echo=FALSE}
ggplot(sjsd, aes(x=event, y=happiness))+
  geom_boxplot(fill="red", outlier.color = "green", varwidth = TRUE)+
  labs(x="Participating in LGBT events", y="Happiness", title="Boxplot of happiness expereinced from attending an event")+
  coord_flip()+
  theme_bw()
```
