---
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    template: ./resources/aog-latex-ms.tex
  word_document:
    reference_docx: ./resources/aog_word_style.docx
fontfamily: mathpazo
fontsize: 11pt
anonymous: false
endnotes: false
pagenumber: 1
bibliography: ../project.bib
biblio-style: ./resources/ajs.bst
title: LGBT Happiness
author: Chandler Gotfried
- affiliation: University of Oregon, Sociology
  name: Aaron Gullickson
- affiliation: Some Research University
  name: My co-author
keywords: keywords
thanks: Thanks to people and stuff
abstract: This is a test abstract
---

```{r, include=FALSE}
load("../../analysis/output/analytical_data.RData")
library(haven)
library(ggplot2)
library(knitr)
library(texreg)
library(tinytex)
```

# Introduction

In movies and television shows, we constantly see parents, friends, neighbors, and others judge an individual for coming out or finding out the indiviudal is LGBT. It gives LGBT individuals a false sense of what actually happens when coming out to peers. Although the movies may make it seem like a scary experience, in reality, it is a breath of fresh air. In 2010, however, our society was inbetween whether or not it supported LGBT indiviudals. America was almost split with a few more leaning in the support same sex indiviudals and relationships. This survey was created to see how the LGBT community felt being in the American society. LGBT individuals coming out to their peers will feel more support, happiness, and overall enjoyment in life because they are able to be who they are. This data should show that although society is not perfect and has not fully accepted the LGBT community, there has been a lot of progress made. The data is from 2010 so we should be able to notice a difference in how individuals felt then compared to how we see the LGBT community act today. Using this data construction, we are going to analyze the overall happiness of individuals that disclose their sexual identity with neighbors, family, and friends and whether it is better to come out than hold it in.

# Data and Methods

The data was collected using self reported surveys in 2010. The original survey was a 105 item survey and was administered to over 5000 people. The strategy of data collection was through a variety of strategies, includng: venue-based sampling at strategic events, snowball sampling, respondent-driven sampling, and the internet. The initial data set comprised of 4953 observations and 304 variables from all sexual identities. After recoding and subsetting, we ended with 10 variables and 3241 observations and 10 variables and only accounted for LGBT responses, not heterosexual responses. This is due to someone being heterosexual and being asked who they came out to which does not make sense. 

Happiness was a combination of two questions: Over the past week, how many times have you felt happy and how many times have you enjoyed life? These we felt were similar so we combined them and subtracted two to make zero our base start. This is our dependent variable for our analysis. We combined another variable from two other questions: How connected do you feel to the LGBT community as a whole and how strong is your bond with others in the LGBT community? We used the same technique as the happiness variable and subtracted two to make our zero our base start. Other variables such as coming out to friends, family, and neighbors were given named labels rather than a numbered order. The same sex marriage and military data was given a true or false code rather than a 1 or 0 code. The rest of the data was left in numbered variables with a different variable name that makes it easier to understand. All the data but the two true or false variables were conducted using a 4,5, or 6-point likert scales making them ordinal variables. To focus on the LGBT community data, anyone who responded as straight was dropped from the subsetted data. This would help reduce biases from possible anti-LGBT thoughts or ideas from straight individuals especially since it is before being LGBT was accepted. 

We calculated some univariate models to better understand what a few of our variables looked like before running mean difference boxplots. In figure 1, we see that a majority of people came out to all of their family members while some and most as well as none and about half were faily equal in responses. Figure 2 was a comparative barplot to show the percentage of individuals who support same sex marriage and military members. The results were less than I had anticiapted. Only around 95% said they are in support. Since we did remove heterosexual data from the datasets, one would have expected at least 99%, if not 100%, of individuals would be in favor of both same sex marriage and mititary members. In figure 3, the histogram shows that individuals are happy a lot (4) to most (6) of the time while very few are never (0) or somtimes (2) happy. Being that this data is from 2010, this is great becasue 2010 was a struggle for the LGBT community to really be recognized as equal to heterosexual community. It shows the positive views that the LGBT community has in a darker period of time. In figure 4, we show the support of family members for LGBT members. The histogram shows that family members are supportive of LGBT members and there is a steady decline on the left tail since we are reaching zero.  

# Results

Figure 1 shows that for those coming out to all of their family members, they feel more supported by their families. As less family members are told about them being LGBT, the less they feel supported by family members. This is how I would have viewed the model looking. A reason we see this is because families are supportive of their children and other memebers of the family, most of the time. To get a better idea of whether this was a coincidence or not, we created another boxplot to show whether coming out to family members produced more happiness. By looking at happiness of the LGBT individual, we can understand if the family members are saying one thing while showing a different physical or vocal action. Figure 2 shows that those who come out to their families are actually happier than those who do not. This means that the families support could be genuine for most cases. There is a common theme of happiness and coming out to family members combined with their support. When LGBT individuals did not come out to their families, they felt less support. This is true because how are your family members suppose to support you if they do not know that you are a part of the LGBT community. Figure 3 changes from family to the LGBT individual's neighborhood. 

We start by viewing whether the LGBT individual told their neighbors and how they feel about the homophobia in the neighborhood. The boxplot shows that individuals feel that their neighbors are less homophobic when they come out to them then when they do not come out. The relationship could show that an LGBT individual feels that a majority of people are homophobic and there for when they realize that someone is fine with their sexual identity, the preconcieved notion of them being homophobic is lessened or gone entirely. The preconcieved notion is based on how they have been treated over the years since LGBT has become a large battle for rights. This does relate into the happiness they feel when they come out to their nieghbors. Figure 4 shows that although many still have fears about their negihbors, they experience more happiness when they come out. It may not be the same level as their family members, but that is to be expected since the neighbors are more friends than actually related (unless their family lives ont he same block as them). Like figure 2, figure 4 shows that when the individual does not come out they are less happier. 

Going to events may help build a relationship among LGBT individuals. Figure 5 displays that when an individual attends a LGBT event, they are more likely to feel closer to the LGBT community. Even just attending one event a year can increase the bond they have with the community. Those who never attend, feel more disconnect to the LGBT community. These results can be explained by thinking about a single individual compared to a community. When someone is alone, they feel lonely and disconnected but when inserted into a group of people with similar identites, they are more likely to be happier. For figure 6 we test whether this is true. When comparing happiness with attending an event, we see the previous idea is true. When someone attends an event, even if it is just one event in a year, they feel happier while someone who does not attend an LGBT event feels less happy. Again, this is because they are with a group of people with similar interests. 

# Conclusions

For the 6 boxplots, we have found that when someone comes out to family and neighbors or is engaged with the LGBT community, they are, on average, happier than those who do not come out or attend events. Also those who come out feel more support and less prejudice for being LGBT by family and neighbors. The models show that coming out is a good experience and has a positive effect in the LGBT individual's life. There were some limitations to the data and research conducted. The survey was based on feelings and thoughts. It is hard to judge the neighborhoods thoughts about homophobia and there is no proof unless explicitly stated. Also, a family member being supportive is hard to notice because humans have become good at hiding their true emotions and thoughts. You can not base merely off of what you feel or think.

# References

```{r barplot1, echo=FALSE}
ggplot(sjsd, aes(x=out_family))+
  geom_bar()+
  labs(x="Coming out to family members", y="Frequency", title="Distribution of coming out to family members")+
  theme_bw()
```

```{r compbarplot, echo=FALSE}
percent <- cbind(prop.table(table(sjsd$marriage)), prop.table(table(sjsd$military)))*100
barplot(percent, beside=TRUE, names.arg=c("Same-sex military","Gay marriage"), 
        las=1, main="Support same sex marriage and military members", ylab="Percent of reponses for support",
        col=c("darkgreen", "yellow"), legend.text=c("No","Yes"), cex.names="0.7")
```

```{r histogram1, echo=FALSE}
ggplot(sjsd, aes(happiness))+
  geom_histogram(binwidth=1, col="black")+
  labs(x="Happiness experienced",y="Frequency",title="Histogram of happiness experienced")+
  theme_bw()
```

```{r histogram2, echo=FALSE}
ggplot(sjsd, aes(fam_support))+
  geom_histogram(binwidth=1, col="green")+
  labs(x="LGBT family support",y="Frequency",title="Histogram of family support for LGBT members")+
  theme_bw()
```


```{r boxplot1, echo=FALSE}
ggplot(sjsd, aes(x=reorder(out_family, happiness, median), y=fam_support))+
  geom_boxplot(fill="gray", outlier.color = "black", varwidth = TRUE)+
  labs(x="Coming out to family members", y="Family support", title="Boxplot of family support after coming out to family members")+
  coord_flip()+
  theme_bw()
```


```{r boxplot2, echo=FALSE}
ggplot(sjsd, aes(x=reorder(out_family, happiness, median), y=happiness))+
  geom_boxplot(fill="skyblue", outlier.color = "red", varwidth = TRUE)+
  labs(x="Coming out to family members", y="Happiness experienced", title="Boxplot of happiness experienced after coming out to family members")+
  coord_flip()+
  theme_bw()
```

```{r boxplot3, echo=FALSE}
ggplot(sjsd, aes(x=out_neighbors, y=neigh_phobia))+
  geom_boxplot(fill="yellow", outlier.color = "green", varwidth = TRUE)+
  labs(x="Coming out to neighbors", y="Neighborhood phobia", title="Boxplot of coming out to neighbors and homophobia in the neighborhood")+
  coord_flip()+
  theme_bw()
```


```{r boxplot4, echo=FALSE}
ggplot(sjsd, aes(x=out_neighbors, y=happiness))+
  geom_boxplot(fill="orange", outlier.color = "blue", varwidth = TRUE)+
  labs(x="Coming out to neighbors", y="Happiness experienced", title="Boxplot of coming out to neighbors and happiness")+
  coord_flip()+
  theme_bw()
```


```{r boxplot5, echo=FALSE}
ggplot(sjsd, aes(x=event, y=lgbt_bond))+
  geom_boxplot(fill="red", outlier.color = "green", varwidth = TRUE)+
  labs(y="Bond felt with LGBT community", x="Participates in LGBT events", title="Boxplot of LGBT events attended and\nthe bond felt with LGBT community")+
  coord_flip()+
  theme_bw()
```


```{r boxplot6, echo=FALSE}
ggplot(sjsd, aes(x=event, y=happiness))+
  geom_boxplot(fill="red", outlier.color = "green", varwidth = TRUE)+
  labs(x="Participating in LGBT events", y="Happiness", title="Boxplot of happiness expereinced from attending an event")+
  coord_flip()+
  theme_bw()
```
