---
title: "Analysis for Project"
output: 
  html_document: 
    toc: yes
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
source("useful_functions.R")
load("output/analytical_data.RData")
library(ggplot2)
library(tidyverse)
library(mice)

```

# Introduction
<a href="#top">Back to top</a>

Use this R Markdown to perform the main analysis for the project. I use this basically as a lab notebook. It contains the main analysis and a variety of sensitivity analysis. The code in this documents serves as a baseline for the eventual tables and figures that will go into the paper. At the same time it will serve as a record of all supplementary analyses performed.


```{r barplot1, echo=FALSE}
ggplot(sjsd, aes(x=out_family))+
  geom_bar()+
  labs(x="Coming out to family members", y="Frequency", title="Distribution of coming out to family members")+
  theme_bw()
```

```{r compbarplot, echo=FALSE}
percent <- cbind(prop.table(table(sjsd$marriage)), prop.table(table(sjsd$military)))*100
barplot(percent, beside=TRUE, names.arg=c("Same-sex military","Gay marriage"), 
        las=1, main="Support same sex marriage and military members", ylab="Percent of reponses for support",
        col=c("darkgreen", "yellow"), legend.text=c("No","Yes"), cex.names="0.7")
```

```{r histogram1, echo=FALSE}
ggplot(sjsd, aes(happiness))+
  geom_histogram(binwidth=1, col="black")+
  labs(x="Happiness experienced",y="Frequency",title="Histogram of happiness experienced")+
  theme_bw()
```

```{r histogram2, echo=FALSE}
ggplot(sjsd, aes(fam_support))+
  geom_histogram(binwidth=1, col="green")+
  labs(x="LGBT family support",y="Frequency",title="Histogram of family support for LGBT members")+
  theme_bw()
```


```{r boxplot1, echo=FALSE}
ggplot(sjsd, aes(x=reorder(out_family, happiness, median), y=fam_support))+
  geom_boxplot(fill="gray", outlier.color = "black", varwidth = TRUE)+
  labs(x="Coming out to family members", y="Family support", title="Boxplot of family support after coming out to family members")+
  coord_flip()+
  theme_bw()
```


```{r boxplot2, echo=FALSE}
ggplot(sjsd, aes(x=reorder(out_family, happiness, median), y=happiness))+
  geom_boxplot(fill="skyblue", outlier.color = "red", varwidth = TRUE)+
  labs(x="Coming out to family members", y="Happiness experienced", title="Boxplot of happiness experienced after coming out to family members")+
  coord_flip()+
  theme_bw()
```

```{r boxplot3, echo=FALSE}
ggplot(sjsd, aes(x=out_neighbors, y=neigh_phobia))+
  geom_boxplot(fill="yellow", outlier.color = "green", varwidth = TRUE)+
  labs(x="Coming out to neighbors", y="Neighborhood phobia", title="Boxplot of coming out to neighbors and homophobia in the neighborhood")+
  coord_flip()+
  theme_bw()
```


```{r boxplot4, echo=FALSE}
ggplot(sjsd, aes(x=out_neighbors, y=happiness))+
  geom_boxplot(fill="orange", outlier.color = "blue", varwidth = TRUE)+
  labs(x="Coming out to neighbors", y="Happiness experienced", title="Boxplot of coming out to neighbors and happiness")+
  coord_flip()+
  theme_bw()
```


```{r boxplot5, echo=FALSE}
ggplot(sjsd, aes(x=event, y=lgbt_bond))+
  geom_boxplot(fill="red", outlier.color = "green", varwidth = TRUE)+
  labs(y="Bond felt with LGBT community", x="Participates in LGBT events", title="Boxplot of LGBT events attended and\nthe bond felt with LGBT community")+
  coord_flip()+
  theme_bw()
```


```{r boxplot6, echo=FALSE}
ggplot(sjsd, aes(x=event, y=happiness))+
  geom_boxplot(fill="red", outlier.color = "green", varwidth = TRUE)+
  labs(x="Participating in LGBT events", y="Happiness", title="Boxplot of happiness expereinced from attending an event")+
  coord_flip()+
  theme_bw()
```
